%************************************************
\section{Introduction}
\label{sec:introduction}
%************************************************

Particles in various forms - ranging from raw materials to food grains and pharmaceutical powders - 
play a major role in a variety of industries, including process industry and metallurgy. 
Discrete Element Method ($DEM$) simulations are widely used to picture particle
behaviour in these granular processes.\\
$LIGGGHTS$ ($LAMMPS$ improved for general granular and granular heat transfer
simulations) is one of the most powerful open source $DEM$ simulation software packages available. 
The models it can analyze are described in detail in the literature, see Kloss
et al. \cite{RefWorks:136}, while a useful example is provided by the shear cell tester 
simulation developed by Aigner et al. \cite{RefWorks:139}.\\
This approach try to solve the issue of particle-particle interaction. The
parameters, empirically by nature, that depict this phenomenon are challenging
to obtain experimentally.
From the experimental point of view, we are focusing
on the bulk behaviour of the materials analysed.
From that we investigated the relationship with the particle-particle $DEM$
contact parameters.
It was out of scope to investigate the properties of each
particle separately, like shape, Young modulus ($E$), coefficient of Poisson ($\nu$) of each sample.\\
Nevertheless, the $DEM$ requires defining these and other attributes for each
single particle.
In our study, we assigned the same particles parameters, except for the radius, to all the 
particles in each simulation. 
In other words, the $DEM$ attributes may vary comparing different 
numerical setups, but are kept constant for each of simulation. 
Further, we tried to obtain simulations ideally perform, with the correct parameters, 
the same macroscopic behaviour of the experiments, the static angle of repose
($AOR$) and Schulze ring shear cell tester ($SRSCT$). That allowed us to later
compare numerical and experimental results, as suggested by Ai et al.
\cite{RefWorks:131}.\\
We could identify the most suitable value for each $DEM$ parameter 
investigated performing huge numbers of simulations. Each will have a different
value.
For instance, for the coefficient of rolling friction ($\mu_r$), ranging from
$0.01$ to $1.00$, a reasonable approach would involve $100$ simulations.
%\input{tables/08DEMparameters}
Regrettably, as stated by Hoehner et al. \cite{RefWorks:86}, all the parameters listed in table \ref{tab:08DEMparameters}
contribute to define the numerical bulk behaviour. Performing and investigate the 
more than $10^8$ simulations required was out of the scope of this paper.
Instead, as suggested by Vaferi et al. \cite{RefWorks:150} and Witten et al.
\cite{RefWorks:174}, we harnessed Artificial Neural Networks ($NN$) for their
stability and reliability with non-linear systems like ours.
Furthermore, the main aim of this work was to improve the characterization 
of several $DEM$ parameters for non-spherical particles. 
From the performed simulations bulk representative parameters were extracted. 
They provide the information for the output layer of the $NN$. Instead the $DEM$ 
parameters of the same simulations provided the information for the input layer. 
Once trained, these $NN$ were fed with random combinations of $DEM$ parameters
(about 6M), and they provided numerical bulk representative parameters for each
of these combinations.
Those were compared with the experimental results. A portion of the combinations
(ca. 0.1\%) had parameters matching with the experiments, i.e. the ratio of the $NN$ behaviour
values over the experimental values differed less than $5\%$, as suggested by
Oberkampf et al. \cite{RefWorks:160}.
We kept these combinations as working solutions. \\
Since this study was supported by the metallurgical industry, the material examined was  sinter fine (0-3.15 mm).
Eventually, all the un-cohesive materials that can be tested through the $AOR$
and $SRSCT$ could be numerically characterized through this workflow, because no
further hypothesis have been imposed.
This flexibility would allow extending the procedure to different granular materials, further than the ones examined.
In the next section we will present the pre-requisites enforced. 
First, the setups we operated to experimentally define the materials. 
Later, the portion of the $DEM$ theory we focused onto. 
Then, the typology of $NN$ we harnessed for this work. 
Furthermore, a detailed methodology is presented. Finally, we show our results.
\input{tables/08DEMparameters}
