\section{Results and discussion}
\label{sec:results}
%************************************************

\subsection{Experiments}
\label{subsec:experiments}

Initially, experimental values identifying the bulk behavior, $\mu_{psh}$, $\mu_{sh}$ and $\rho_{b}$, 
for sinter fine have been acquired through the $SRSCT$, e.g. in Table
\ref{tab:05sinterTableExperimental}
these values for three load conditions are presented.
In the $\mu_{psh}$ a descending path is evident. 
Instead, the $\mu_{sh}$ is oscillating.
The $\rho_b$ presents a clear average of $1760 [kg/m^3]$ with a $42 [kg/m^3]$
deviation.
The stress path for the second load condition of Table
\ref{tab:05sinterTableExperimental} is shown in Fig.
\ref{fig:20experimental}.
In the first 300 seconds the $\sigma_n$ was kept constant. After 250 seconds a
plateau was reached. 
The $\mu_{psh}$ was calculated as average of the $\mu_{ie}$ in this plateau.
Later, the $\sigma_n$ was reduced to $80 \%$ of its initial value.
After approximately 30 seconds, a second plateau started.
As average of $\mu_{ie}$ in this second plateau we obtained $\mu_{sh}$.
%\input{tables/05sinterTableExperimental}
Later, two $AOR$ test have been performed, thus identifying an average angle of
$38.85 ^\circ$.
We also realized the sieving, obtaining the radius ($R$) mean and standard
deviation, already shown in Table \ref{tab:09DEMFixedinputvalues}.
\input{images/texCaller/40experimentalsimulation}
\input{tables/05sinterTableExperimental}

\subsection{DEM Simulations}
\label{subsec:simulations}

For sinter fine 546 shear cell and 81 static angle of repose simulations have
been realized with the variations described in table
\ref{tab:10DEMVariableinputvalues}.
A representative stress path can be seen in Fig. \ref{fig:21simexample}.
Although the duration is smaller by two order of magnitude, the stress path is
comparable to the experimental one, especially the plateaux.
They were clearly relevant because there we collected the numerical bulk
behaviour representative values.\\
The computational time resulted in 1 hour with 32 AMD cores for a benchmark
shear cell simulation and 9 hours for a benchmark $AOR$ simulation, both with 50K particles. 
Simulations with large $dCylDp$ required a greater time amount (e.g. with 400K
particles about 12 hours for the shear cell). \\
%\input{images/texCaller/21simexample}

\subsection{ANN model development}
\label{subsec:annmodeldev}

First, we controlled the regression of the bulk behaviour parameters, e.g. the
$\mu_{psh}$, see Fig. \ref{fig:22regression}, where the corresponding plot for
the $NN$ with the maximum $R^2$ in shown. Each circle represents one of the 546
simulations.
The plot presents a consistent agreement between the $DEM$ results distribution
(T in the legend) and the $NN$ regression (or fitting) line.
% \input{images/texCaller/22regression}
The linear relationship between the
training values have been evaluated in Table \ref{tab:06inputRelationshipTable}.
The clearest connections were between $\mu_s$ and $\mu_{psh}$, and
$\rho_p$ and $\rho_b$.
Instead, for $\mu_{sh}$ and $AOR$ the $\mu_r$ balanced the influence of the 
$\mu_s$, and further parameters were worthly correlated. \\
% \input{tables/06inputRelationshipTable}
Then we observed how the $R^2$ changed with the different number of neurons for
the $\mu_{psh}$.
Then we observed how the $R^2$ changed with the different number of neurons for the $\mu_{psh}$. 
In this case we reached a $R^2 = 0.96$ for a $NN$ with fifteen neurons. 
Increasing the number of neurons did not improve the $R^2$, that even started to oscillate with the neuron number. 
Later, we processed the random combinations (table
\ref{tab:10DEMVariableinputvalues}) with the $NN$.
The $NN$ evaluation was incredibly faster compared to the $DEM$ simulations. The
individuation of all the tabbed $DEM$ combinations for the shear cell did not take more than a few seconds on a single core. 
We represented the tabbed combinations ($TC1$) for one load condition of the
shear cell ($\sigma_n=10070 ~[Pa]$, $P=1.0$) in Fig.
\ref{fig:24radarpirker1schulze10070}.
% \input{images/texCaller/29schulzeradarandcloud}
Here, the minimum and maximum values, together with the mean and the confidence
range, provided by the square deviation, are shown. Notably, the confidence range is large, 
especially for the $COR$, highlighting its scarce influence over the characterization. 
Instead, both the $\rho_p$  and the $\mu_s$ show a narrow confidence range, 
displaying at the same time their influence and the validity of this procedure to find valid $DEM$ parameters. 
That agrees with the examination of the ratio of the standard deviation to the
range, see table \ref{tab:13DEMvalidvalues}.
Further, we could see how different $DEM$ parameters
combinations could reproduce the experimental behaviour and evaluate their mutual dependencies. 
This is clearer in a cloud plot, as in Fig. 
\ref{fig:25cloudpirker1schulze10070}. While the $COR$ varied, multiple
combinations ($250407 --> 4\% $ of the total) of $\mu_s$ and $\mu_r$ reproduced
the experimental behaviour.
This underlines once more their correlation, as already stated by Wensrich and 
Katterfeld \cite{RefWorks:87}.
To further demonstrate the validity of the procedure, we modified the product
coefficient. In the first attempt we set it to $P=0.8$ and we obtained another
series of tabbed combinations ($TC2$).
We can see in the radar plot in Fig.
\ref{fig:26radarpirker08schulze10070} that the confidence range is narrower
compared to $P=1.0$, while in the cloud plot in Fig. 
\ref{fig:27cloudpirker08schulze10070} the area
appears larger, although slightly less densely populated. Finally, for $P=1.2$
and its tabbed combinations ($TC3$) the radar plot in Fig.
\ref{fig:28radarpirker12schulze10070} shows a largely different confidence
range, while the cloud plot in Fig. \ref{fig:30cloudpirker12schulze10070} 
illustrates a smaller area. As expected, the procedure was highly sensible to the variations of the experimental data. 
Thus, it could be effectively handled for a wide range of bulk materials.\\
% \input{images/texCaller/35schulze10070aorradarandcloud}
We then processed the random combinations with the $AOR$ $NN$. In Fig.
\ref{fig:31radarpirker1aor} the radar plot realized with the same criteria as
before can be seen.
In accordance with the theory (Wensrich and Katterfeld \cite{RefWorks:87}), in a simulation dominated
by the particles rolling the coefficient of rolling friction has the maximum influence. 
Further, in the cloud plot in Fig. \ref{fig:32cloudpirker1aor}
we could see that there are valid combinations also with slight $\mu_s$. \\
Finally, we extracted from the $TC1$ values the $AOR$ $NN$ behaviour
and compared it with the experimental one.
As can be seen in the radar plot in Fig.
\ref{fig:33radarpirker1schulze10070aor}, the confidence range is meager, indicating that all the parameters but the $COR$ 
had an important role and the reliability of these parameters combinations to represent the bulk behaviour. 
Also in the cloud plot in Fig. \ref{fig:34cloudpirker1schulze10070aor} we
observed a condensed distribution of valid parameters.
From the initial 6250000 combinations, only 3884 of them were valid (0.0621 \%),
see table \ref{tab:13DEMvalidvalues}.
\input{images/texCaller/22regression}
\input{tables/06inputRelationshipTable}
\input{tables/13DEMvalidvalues}
%\input{images/texCaller/23regressiongraph}
%\input{images/texCaller/29schulzeradarandcloud}
%\input{images/texCaller/35schulze10070aorradarandcloud}
\input{images/texCaller/36schulzeradar}
\input{images/texCaller/37schulzecloud}
\input{images/texCaller/38schulze10070aorradar}
\input{images/texCaller/39schulze10070aorcloud}


%\input{images/texCaller/24radarpirker1schulze10070}
%\input{images/texCaller/25cloudpirker1schulze10070}
%\input{images/texCaller/26radarpirker08schulze10070}
%\input{images/texCaller/27cloudpirker08schulze10070}
%\input{images/texCaller/28radarpirker12schulze10070}
% \ref{eq:rsquare}.
% \input{equations/rSquare}
% 
% \ref{eq:rootMeanSquareError}.
% \input{equations/rootMeanSquareError}



% \lipsum[1]
% \input{equations/newtonlaw}
% \subsection{ANN identification}
% \label{subsec:annmodeliden}
% \subsection{ANN application}
% \label{subsec:annapplication}
% 
% Later, each of these three trained $NN$ received as insertion $100M$ different
% combinations $DEM-micro$ parameters.
% So, we gained the numerical bulk behavior for each of this combination. 
% We then compared the values of these behaviors against the experimental bulk
% values, $SRSCT$ and $AOR$, obtaining a narrow range of valid DEM-micro
% combinations (about 80K).
% These results have been showed through radar plots (Figs. \ref{fig:15Schulze}
% and \ref{fig:16aorSchulzeIntersectionWorking}).
% To highlight an eventual $clumping$ behavior, we also plot the results in a
% cloud shape, see Fig. \ref{fig:17aorSchulzeIntersectionCloudSFRFCOR}.
% 
% %\input{images/texCaller/14aorSchulzeIntersection}
% \input{images/texCaller/15Schulze}
% % \lipsum[1]
% \input{images/texCaller/16aorSchulzeIntersectionWorking}
% % \input{equations/phi_ps}
% \input{images/texCaller/17aorSchulzeIntersectionCloudSFRFCOR}
