\documentclass[review]{elsarticle}
% \usepackage[utf8]{inputenc}
% \usepackage{subcaption}
% \usepackage{amsmath}
% \usepackage{listings}
% \usepackage{courier}
% \usepackage{tikz}
% \usepackage{graphicx}
% \usepackage{picins}
% \usepackage{epstopdf}
% 
% 
% \usepackage{lipsum}                        % testo fittizio
% 
% \usepackage[nomarkers]{endfloat}
% 
% \newcommand{\listoflstlistings}{\lstlistoflistings}
% \DeclareDelayedFloat{lstlisting}[flol]{\textbf{List of Listings}}
% 
% \lstset{tabsize=2,language=C++,basicstyle=\footnotesize\tt,keywordstyle=\color{blue}\bfseries}

\journal{Powder Technology}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frontmatter}

\title{Identification of DEM Simulation Parameters by Artificial Neural Networks
and Bulk Experiments}

\author[jku]{L.~Benvenuti\corref{cor1}}
\ead{Tel. +43 73224686483}
\ead{luca.benvenuti@jku.at}

\author[dcs]{C.~Kloss}
\ead{christoph.kloss@dcs-computing.com}

\author[jku]{S.~Pirker}
\ead{stefan.pirker@jku.at}

\cortext[cor1]{Corresponding author}

\address[jku]{Johannes Kepler University Linz, Department on Particulate Flow
Modelling, Altenbergerstrasse 69, 4040, Linz, Austria}

\address[dcs]{DCS Computing GmbH, Altenbergerstr. 66a - Science Park, 4040 Linz,
Austria}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In Discrete Element Method ($DEM$) simulations, particle-particle contact laws
determine the macroscopic simulation results. Particle based contact laws, in
turn, commonly rely on semi-empirical parameters, which can be hardly obtained
by direct microscopic measurements.
In this study we present a methodology for the identification of
$DEM$ simulation parameters by linking the macroscopic experimental results to the
microscopic numerical parameters by artificial neural networks.
In a first step, a series
of $DEM$ simulations with varying simulation parameters are used to train a feed
forward artificial neural network by backward propagation reinforcement. In a
second step, this artificial neural network is utilized to predict the
macroscopic ensemble behaviour in dependence of additional sets of particle
based simulation parameters.
As a result, a comprehensive database is obtained,
which links particle based simulation parameters to a specific macroscopic
bulk behaviour of the ensemble.
The trained artificial neural network is able to predict the behaviour of
additional sets of input parameters accurately and highly efficient.
Furthermore, this methodology can be applied to
identify $DEM$ material parameters in a generic way.
For each set of calibration experiments, the training of the neural network has
to be performed just once. 
After the training, the neural network provides a generic link between the macroscopic 
experimental results and the microscopic $DEM$ simulation parameters.
By the help of these experiments, the $DEM$ simulation parameters of a specific
non-cohesive granular material can be identified.

\end{abstract}

\begin{keyword}
Discrete Element Method ($DEM$) Simulations \sep Parameter Identification \sep Artificial Neural Networks
\end{keyword}
\end{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%************************************************
\section{Highlights}
\label{sec:highlights}
%************************************************
\begin{itemize}
  \item{We trained an Artificial Neural Network by DEM simulations with varying
  parameters}
  \item{The Artificial Neural Network then predicts granular bulk behaviour}
  \item{By comparison with bulk experiments DEM simulation parameters are
  identified}
  \item{This DEM parameter identification can be applied to different bulk
  behaviours}
  \item{This DEM parameter identification can be applied to different granular
  materials}
\end{itemize}
%************************************************

%\input{introduction}

%\input{modellingprerequisites}
%\input{methodology}
%\input{resultsdiscussion}
%\input{conclusions}

\section{Acknowledgements}
This study was funded by Christian Doppler Forschungsgesellschaft, Siemens VAI Metals Technologies and Voestalpine Stahl. The authors gratefully aknowledge their support.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{elsarticle-num}
\bibliography{Bibliografia}



\newpage
%\input{appendix}

\newpage
%\input{vitae}

\renewcommand\thefigure{\arabic{figure}}

\end{document}
