% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX root = ../Articolo.tex
% !TEX spellcheck = it-IT

%************************************************
\section{CFD Conference}
\label{sec:cfdconference}
%************************************************

I found very useful and interesting the partecipation to the CFD 2014 Conference in Trondheim.\\
After inputs from the audience, I know now that future presentations of my paper, \textit{Establishing the predictive capabilities of DEM simulations: sliding and rolling friction coefficients of non-spherical particles}, should underline that: 
\begin{itemize}
\item{the real material is polydisperse, eventually showing a granulometric curve;}
\item{the simulations were performed with monodisperse spheres;}
\item{cohesion was not studied;}
\item{which diagrams belong to the experiments and which to the simulations;}
\item{the simulations were 3D;}
\item{the experiment time VS the simulation time;}
\item{the Coefficient of Restitution is an extimation (I am working on it);}
\item{and I should also show some photos of the raw materials.}
\end{itemize}

On the other hand, I attended many lectures, surely the most interesting for my work was held by Prof. Oberkampf, \textit{Concepts and Practice of Verification, Validation, and Uncertainty Quantification}. \\
A lot of people presented about packed and fluidized bed. Unfortunately the large majority were only simulation works performed with FLUENT. The few with experimental work were not extremely strict about uniform boundary conditions.
Furthermore a post-doc (Dr. Pereira) of Prof. Cleary team presented a work concerning dynamic AOR with DEM. It involved mainly segregation in bi-disperse bulk, but I will study it more carefully study to see if I can find some suggestions.\\