\begin{abstract}
Discrete Element Method ($DEM$) simulations are widely used to model and understand particle behavior. 
It is important to note that each combination of DEM-micro parameters gets different bulk-macro behavior.
As a consequence, a straight-forward trial-and-error calibration procedure is prohibitively computationally expensive to fathom the micro-macro transition relationship.
A limited number of combinations have been simulated, through 2000 shear cell numeric test and 300 $static-angle-of-repose$ ($SAOR$) numeric test.
The DEM parameters of the simulations have been used as inputs of feed forward Multilayer Perceptron Neural Networks ($MLPNN$), while the bulk values and behavior as targets for the Neural Networks ($NN$).
A backpropagation reinforcement learning training algorithm has been used (scaled conjugate gradient).
A NN has been created for each bulk parameter investigated.
15\% of the simulations have been excluded from the training processes.
They have been used to define per each $NN$ the correct number of neurons in the hidden layer, based on an $R^2$ maximization.
Then each trained $NN$ received as input one million different combinations.
The bulk solids were characterized using shear cell testers. 
The DEM coefficients were obtained by fitting $NN$ outputs to experimental data (within a 5\% error).
Further, we validated the $DEM$ parameters by means of $SAOR$ experiments and $SAOR$ simulations-trained NN.
The validation agreement was also within reliable limits (5\% error).
The calculated $DEM$ coefficients of iron ore, limestone and silibeads accord well with published data and in-house experiments. 
\end{abstract}


\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Meshless methods (DEM) \sep Rheology \sep experimental validation studies \sep process industries \sep process metallurgy \sep LIGGGHTS \sep Material characterization \sep Artificial Neural Networks
%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}