\section{Results and discussion}
\label{sec:results}
%************************************************

\subsection{Experiments}
\label{subsec:experiments}

Initially, experimental values identifying the bulk behavior, $\mu_{e-psh}$, $\mu_{e-sh}$ and $\rho_{b}$, 
for sinter fine have been acquired though the SRSCT, see Table \ref{tab:05sinterTableExperimental}. 
A representative stress path can be seen in Fig. \ref{fig:20experimental}.
\input{tables/05sinterTableExperimental}
\input{images/texCaller/20experimental}
Later, two AOR test have been performed, given an average angle of $38.85
^\circ$.
We also realized the sieving.

\subsection{DEM Simulations}
\label{subsec:simulations}

For sinter fine 546 shear cell and 81 static angle of repose simulations have
been realized with the variation described in Tab.
\ref{tab:10DEMVariableinputvalues}.
A representative stress path can be seen in Fig. \ref{fig:21simexample}.
\input{images/texCaller/21simexample}
The computational time resulted in 1 hour with 32 AMD cores for a benchmark
shear cell simulation and 9 hours for a benchmark $AOR$ simulation, both with 50K particles. 
Simulations with large $dCylDp$ required a greater time amount (e.g. with 400K
particles $\~ 12 hours$ for the shear cell). \\




\subsection{ANN model development}
\label{subsec:annmodeldev}

First, we present the regression plot of a bulk behaviour parameter, e.g. the
$\mu_{e-psh}$, see Fig. \ref{fig:22regression}, where the regression plot for
the $NN$ with the maximum $R^2$ in shown. Each circle represents a simulation. 
The plot presents a consistent agreement between the DEM results distribution and the NN regression line.
\input{images/texCaller/22regression}
The linear relationship between the
training values have been evaluated in Table \ref{tab:06inputRelationshipTable}.
\input{tables/06inputRelationshipTable}
Then we show how the $R^2$ changed with the different number of neurons. The
straight line, referred only to the test simulations, is more sensible to
variations of number of neurons, see Fig. \ref{fig:23regressiongraph}.
\input{images/texCaller/23regressiongraph}
Thus, we selected the $NN$ with the maximum $R^2$ in the test line, as stated in the methodology.
Later, we processed the random combinations (Tab.
\ref{tab:10DEMVariableinputvalues}) with the $NN$.
The $NN$ evaluation was incredibly faster compared to the $DEM$ simulations. The
individuation of all the tabbed $DEM$ combinations for the shear cell did not take more than a few seconds on a single core. 
We represented the tabbed combinations for one load condition of the shear cell in Fig.
\ref{fig:24radarpirker1schulze10070}.
\input{images/texCaller/29schulzeradarandcloud}
Here, the minimum and maximum values, together with the mean and the confidence
range, provided by the square deviation, are shown. Notably, the confidence range is large, 
especially for the $COR$, highlighting its scarce influence over the characterization. 
Instead, both the $\rho_p$  and the $\mu_s$ show a narrow confidence range, 
displaying at the same time their influence and the validity of this procedure to find valid $DEM$ parameters. 
Especially, we could see how different $DEM$ parameters combinations could reproduce the experimental 
behaviour and evaluate their mutual dependencies. 
This is clearer in a cloud plot, as in Fig. 
\ref{fig:25cloudpirker1schulze10070}. While the $COR$ varied, multiple
combinations ($250407 --> 4\% $ of the total) of $\mu_s$ and $\mu_r$ reproduced
the experimental behaviour.
To further demonstrate the validity of the procedure, we modified the product
coefficient. In the first attempt we set it to $P=0.8$. We can see in the radar plot in Fig. 
\ref{fig:26radarpirker08schulze10070} that the confidence range is narrower
compared to $P=1.0$. Instead in the cloud plot in Fig. 
\ref{fig:27cloudpirker08schulze10070} the area
looks larger, although slightly less densely populated. Finally, for $P=1.2$ the radar plot in Fig.
\ref{fig:28radarpirker12schulze10070} shows a completely different confidence
range, while the cloud plot in Fig. \ref{fig:30cloudpirker12schulze10070} 
illustrates a largely smaller area. As expected, the procedure was highly sensible to the variations of the experimental data. 
Thus, it could be effectively handled for a wide range of bulk materials.\\
\input{images/texCaller/35schulze10070aorradarandcloud}
We then processed the random combinations with the $AOR$ $NN$. In Fig.
\ref{fig:31radarpirker1aor} the radar plot can be seen. In accordance with the
theory (Wensrich and Katterfeld \cite{RefWorks:87}), in a simulation dominated
by the particles rolling the coefficient of rolling friction has the maximum influence. 
Further, in the cloud plot in Fig. \ref{fig:32cloudpirker1aor}
we could see that there are valid combinations also with slight $\mu_s$. \\
Finally, we extracted from the tabbed combinations values ($P=1.0$) the $AOR$ $NN$ behaviour and compared it with the experimental one. 
As can be seen in the radar plot in Fig.
\ref{fig:33radarpirker1schulze10070aor}, the confidence range is meager, indicating that all the parameters but the $COR$ 
had an important role and the reliability of these parameters combinations to represent the bulk behaviour. 
Also in the cloud plot in Fig. \ref{fig:34cloudpirker1schulze10070aor} we
observed a condensed distribution of valid parameters.
From the initial 6250000 combinations, only 3884 of them are valid (0.0621 \%).







%\input{images/texCaller/24radarpirker1schulze10070}
%\input{images/texCaller/25cloudpirker1schulze10070}
%\input{images/texCaller/26radarpirker08schulze10070}
%\input{images/texCaller/27cloudpirker08schulze10070}
%\input{images/texCaller/28radarpirker12schulze10070}
% \ref{eq:rsquare}.
% \input{equations/rSquare}
% 
% \ref{eq:rootMeanSquareError}.
% \input{equations/rootMeanSquareError}



% \lipsum[1]
% \input{equations/newtonlaw}
% \subsection{ANN identification}
% \label{subsec:annmodeliden}
% \subsection{ANN application}
% \label{subsec:annapplication}
% 
% Later, each of these three trained $NN$ received as insertion $100M$ different
% combinations $DEM-micro$ parameters.
% So, we gained the numerical bulk behavior for each of this combination. 
% We then compared the values of these behaviors against the experimental bulk
% values, $SRSCT$ and $AOR$, obtaining a narrow range of valid DEM-micro
% combinations (about 80K).
% These results have been showed through radar plots (Figs. \ref{fig:15Schulze}
% and \ref{fig:16aorSchulzeIntersectionWorking}).
% To highlight an eventual $clumping$ behavior, we also plot the results in a
% cloud shape, see Fig. \ref{fig:17aorSchulzeIntersectionCloudSFRFCOR}.
% 
% %\input{images/texCaller/14aorSchulzeIntersection}
% \input{images/texCaller/15Schulze}
% % \lipsum[1]
% \input{images/texCaller/16aorSchulzeIntersectionWorking}
% % \input{equations/phi_ps}
% \input{images/texCaller/17aorSchulzeIntersectionCloudSFRFCOR}
